Appendix to Public Gender Egalitarianism: A Dataset of Dynamic Comparative

### 2022-01-04 paper/pge_appendix.Rmd
add plot of observations by country-year for #26; consider moving to text?

>>>>

\pagebreak

```{r obs_by_cy, fig.height = 9, fig.width = 6.5, fig.cap = "Source Data Observations by Country and Year \\label{obs_by_cy}"}
dcpo_input_raw_poliwork1 %>% 
  mutate(country = str_replace(country, "’", "'")) %>% 
    distinct(country, year, item, cc_rank) %>% 
    group_by(country, year) %>% 
    summarize(n = n(),
              cc_rank = cc_rank) %>% 
    ungroup() %>% 
    distinct() %>% 
    ggplot(aes(x = year, 
               y = forcats::fct_reorder(country, cc_rank),
               fill = n)) + 
    geom_tile() +
    scale_fill_stepsn(colors = rev(hcl.colors(7, "inferno")),
                      n.breaks = 7,
                      show.limits = TRUE,
                      right = FALSE,
                      name = "Observations") +
    labs(x = NULL, y = NULL) +
    scale_x_continuous(breaks=seq(1972, 2020, 4)) +
    theme(legend.justification=c(0, 0), 
          legend.position=c(0.01, 0.01),
          axis.text.y  = element_text(size = 7)) #+
    # ggtitle("Source Data Observations by Country and Year")
```
